強化学習モデル: 最尤推定

### 2022-11-02 how-to-cognitive-modeling-rl1.Rmd
update

```{r}
sub01 %>% 
	filter(trial_type == "html-button-response") %>% 
  mutate(trial = 1:80, 
         s1_prob = rep(c(0.8,0.2),each = 40),
         reward = ifelse(button_pressed == 0, reward_s1, reward_s2)) %>% 
  select(trial,choice=button_pressed, rt, reward, s1_prob,reward_s1, reward_s2)
```

>>>>

```{r}
sub01 %>% 
	filter(trial_type == "html-button-response") %>% 
  mutate(trial = 1:80, 
         s1_prob = rep(c(0.2,0.8),each = 40),
         reward = ifelse(button_pressed == 0, reward_s1, reward_s2)) %>% 
  select(trial,choice=button_pressed, rt, reward, s1_prob,reward_s1, reward_s2)
```
